Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola

### 2023-02-09 Manuscript/manuscript_files/figures.tex

Figure 2: Partial effect of distance from a) honey bee apiaries (at edge of the field), b) leafcutter shelters, and c) female bay position on visitation rates, with shaded regions and line ranges showing 95\% CIs. Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).

@@

Figure 5: Simulated effect of honey bee distance and leafcutter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation. Shaded areas shown in a \& b are 95\% quantiles for the simulations. Lines on panels c - f are isolines of constant seed size (c, e) or yield (d, f).

>>>>

Figure 2: Partial effect of distance from a) honey bee apiaries (at edge of the field), b) leafcutting bee shelters, and c) female bay position on visitation rates, with shaded regions and line ranges showing 95\% CIs. Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).

@@

Figure 5: Simulated effect of honey bee apiary distance and leafcutting bee shelter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation. Shaded areas shown in a \& b are 95\% quantiles for the simulations. Lines on panels c - f are isolines of constant seed size (c, e) or yield (d, f).
